Optimal Strategies for Target Volatility Contracts

### 2021-04-10 tex/targetvol.tex
Latex

\usepackage[]{hyperref}
\hypersetup{
	colorlinks=true,breaklinks=true,
	urlcolor= mydarkblue,linkcolor= mydarkblue,citecolor= mydarkgreen,
	pdfauthor={Daluiso, R., Pallavicini, A.},
}
\usepackage[backend=biber,style=authoryear-comp,maxcitenames=2,sorting=nyt,natbib=true,sortcites=false]{biblatex}
\addbibresource{Bib.bib}
%\usepackage{natbib}
%\setcitestyle{authoryear,open={(},close={)}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

@@

\section{Reinforcement Learning}\label{sec:RL}
 Reinforcement Learning (RL) describes how an agent behaves in an environment so to maximize some notion of cumulative reward. The actions of the agent as a function of his observations of the environment are termed the agent policy. In our case the policy is the asset allocation weights $\alpha$, while the rewards are the costs generated by hedging a derivative contract on the TVS. Once the agent is trained, and the optimal policy is selected, we can run a Monte Carlo simulation to calculate the option price on the TVS.

>>>>

\usepackage[]{hyperref}
\hypersetup{
	colorlinks=true,breaklinks=true,
	urlcolor= mydarkblue,linkcolor= mydarkblue,citecolor= mydarkgreen,
	pdfauthor={Daluiso, R., Pallavicini, A., Nastasi, E., Polo, S.},
}
\usepackage[backend=biber,style=authoryear-comp,maxcitenames=2,sorting=nyt,natbib=true,sortcites=false]{biblatex}
\addbibresource{Bib.bib}
%\usepackage{natbib}
%\setcitestyle{authoryear,open={(},close={)}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

@@

\section{Reinforcement Learning}\label{sec:RL}
As we have seen previously the determination of the derivative price on the TVS requires to  solve a stochastic control problem with continuous actions. Among the available standard techniques, Reinforcement Learning (RL) represents a new efficient way to solve stochastic optimal control problems in high dimensions.

 Reinforcement Learning (RL) describes how an agent behaves in an environment so to maximize some notion of cumulative reward. The actions of the agent as a function of his observations of the environment are termed the agent policy.  In our case the policy is the asset allocation weights $\alpha$, while the rewards are the costs generated by hedging a derivative contract on the TVS. Once the agent is trained, and the optimal policy is selected, we can run a Monte Carlo simulation to calculate the option price on the TVS.
